---
title: "A1-A-ArrayOperations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

1. How many rows does the *simplebudget* data have?

2. How many columns?


```{r}

# Write your code and your comments here.
simplebudget = read.csv("simplebudget.csv") 
rows = nrow(simplebudget)
rows

columns = ncol(simplebudget)
columns
# Any plot you generate will be shown in the document.

```

## Question 2

1. What are the classes of each column?

2. What are the names of each column? 

3. What do we use to see the first few lines ?


```{r}

# Write your code and your comments here.

simplebudget = read.csv("simplebudget.csv") 

class(simplebudget$Portfolio)
class(simplebudget$Department.Agency)
class(simplebudget$Y2013.14)

names(simplebudget) 

head(simplebudget)

# Any plot you generate will be shown in the document.

```



## Question 3

1. How many portfolios are represented in the Portfolio column?

2. What are their names?

3. How many rows for each portfolio?

4. What is the total budget for Defence Portfolio?


```{r}

# Write your code and your comments here.

simplebudget = read.csv("simplebudget.csv") 
length(levels(simplebudget$Portfolio))
levels(simplebudget$Portfolio)
summary(simplebudget)
sum(simplebudget$Y2013.14[simplebudget$Portfolio == "Defence Portfolio"])

# Any plot you generate will be shown in the document.

```

## Question 4

What are a few different ways to load data from a text file?

```{r}

# Write your code and your comments here.
read.csv("simplebudget.csv") 

# Any plot you generate will be shown in the document.

```

## Question 5

Find two interesting datasets that are built into R or an R package and describe their shape and contents (using code).  

```{r}

# Write your code and your comments here.
names(ChickWeight)
nrow(ChickWeight)
str(ChickWeight)
summary(ChickWeight) 
head(ChickWeight)
# Any plot you generate will be shown in the document.

```
